Different ML algorithms were used to train models that can detect MW. Many ML algorithms are used for the classification tasks because it is not yet known which algorithm is best suited to train a model that can automatically detect MW. Often, the ML algorithms that are used are from Weka\footnote{https://www.cs.waikato.ac.nz/ml/weka/} \cite{Bixler2015AutomaticPhysiology}\cite{Bixler2015AutomaticAwareness}\cite{Bixler2016AutomaticReadingd}\cite{Bixler2014TowardWanderingd}\cite{Blanchard2014AutomatedLearning}\cite{Gwizdka2019ExploringTasks}\cite{Hutt2017OutClassroom}\cite{Pham2015Attentivelearner:Tracking}, a collection of machine learning algorithms. From these algorithms the best one(s) would be picked. Most studies concluded that Support Vector Machines and Bayesian models performed best. There were also studies that did not use ML algorithms, initial evidence was provided that high-frequency words in lecture videos could be used to detect MW \cite{Jo2017AMind}. These studies investigated whether there is a relation between specific features and MW. It also occurred that ML could not be applied due to the fact that there was too few participants in the study \cite{Gontier2016HowEnvironment}. This resulted in a dataset that was too small to train a model with.

The performance was measured using different metrics of accuracy, for example by using a F$_1$ score, Cohen's kappa or as a percentage based accuracy. Percentage based accuracy can be defined in different ways, which is mostly dependent on the application. For example, percentage based accuracy was defined in one study as the area under the receiver operator characteristic curve \cite{Cheetham2016AutomatedApplication}, but cross-validation accuracy was also used \cite{Mishchenko2015DetectingTespiti}. This makes it hard to compare different studies. Some properties were however also compared within the study. Some results show that there is no significant difference in accuracy between a window size of 5 and 10 seconds \cite{Gwizdka2019ExploringTasks}. This confirms that the optimal window size is not the same for every application and study. This study also showed a significant increase in accuracy over what was achieved in \cite{Bixler2014TowardWanderingd}. As mentioned before, it is important to verify whether MW could also be detected by using equipment that is owned by more people. One study found that a low-end webcam performed as good as an eye tracker \cite{Zhao2017ScalableApproach}. Yet another study achieved an accuracy of 53\% using a mobile device \cite{ISI:000443429900018}, showing a slight decrease in accuracy compared to similar studies using an eye tracker.