\begin{tabularx}{\textheight}{|>{\hsize=.4\hsize}X|>{\hsize=.4\hsize}X|>{\hsize=.4\hsize}X|>{\hsize=.4\hsize}X|>{\hsize=.3\hsize}X|>{\hsize=.4\hsize}X|>{\hsize=.4\hsize}X|>{\hsize=.4\hsize}X}
    \hline
    References & Task & Modalities & Features & Equipment & Reporting MW & ML models & Performance \\
     \hline
     \hline
     Bixler et al. \cite{Bixler2015AutomaticPhysiology} & Reading & Eye gaze, physiology, contextual cues & GGF (46), LGF (23), SC (43), ST (43), CF (11)  & Eye tracker & WP, EP & 13 supervised ML classifiers in Weka & Kappa = 0.19\\
     \hline
     Bixler et al. \cite{Bixler2015AutomaticAwareness} & Reading & Eye gaze & GGF (46), LGF (20) & Eye tracker & Pseudo-random AP, SCR & 10 ML classifiers in Weka & Kappa = 0.45\\
     \hline
     Bixler et al. \cite{Bixler2016AutomaticReading} & Reading & Eye gaze, contextual cues & GGF (46), LGF (23), CF (11) & Eye tracker & WP, EP & 20 supervised ML classifiers in Weka & Kappa = 0.31\\
     \hline
     Bixler et al. \cite{Bixler2014TowardWandering} & Reading & Eye gaze, contextual cues & GGF (30), LGF (19), CF(12) & Eye tracker & WP, EP & 20 supervised ML classifiers in Weka & Kappa = 0.28 (end-of-page), Kappa = 0.17 (within-page)\\
     \hline
     Blanchard et al. \cite{Blanchard2014AutomatedLearning} & Reading & Physiology & SC (43), ST (43), CF (11) & Wearable sensor & WP, EP & Supervised classifiers in Weka & Kappa = 0.22\\
     \hline
     Cheetham et al. \cite{Cheetham2016AutomatedApplication} & Eyes-closed FA meditation & Respiration, heart rate, electrocardiogram, electromyogram, electrodermal acitivity & N/S & Biosensors & SCR & N/S & Accuracy = 85\% (area under the receiver operator characteristic curve)\\
     \hline
     Da Silva et al. \cite{DaSilva2018WanderingWandering} & Maintain access to memory items (letters) while completing math equations & Mouse movements & Time to press start, initiation time, total distance, average speed, speed errors & Regular computer & Probes after each set & Mixed effects logistic regression & N/S\\
     \hline
     Gontier \cite{Gontier2016HowEnvironment} & Various extra-vehicular activities at the Mars Desert Research Station & Heart rate & Measures of heart rate variability & ECG sensor & AP & N/A & This study was only done with 1 participant, so did not mention much in terms of relevant results. \\
     \hline
     Gwizdka \cite{Gwizdka2019ExploringTasks} & Reading & Eye gaze & 27 eye gaze features & Eye tracker & WP & ML classifiers in Weka 3.8 & Accuracy of 73-89\% (might be inaccurate due to resampling)\\
     \hline
     Hutt et al. \cite{Hutt2017OutClassroom} & & & & & & &\\
     \hline
     Jo et al. \cite{Jo2017AMind} & & & & & & &\\
     \hline
     Mishchenko et al. \cite{Mishchenko2015DetectingTespiti} & & & & & & &\\
     \hline
     Pham et al. \cite{Pham2015Attentivelearner:Tracking} & & & & & & &\\
     \hline
     Russel et al. \cite{Russell2016MonitoringEnvironments} & & & & & & &\\
     \hline
     Stewart et al. \cite{Stewart2017FaceComprehension} & & & & & & &\\
     \hline
     Stewart et al. \cite{Stewart2016WheresViewing} & & & & & & &\\
     \hline
     Zhang et al. \cite{ISI:000443429900018} & & & & & & &\\
     \hline
     Zhao et al. \cite{Zhao2017ScalableApproach} & & & & & & &\\
     \hline
    \end{tabularx}